---
title: "homework-4"
author: "Amina Mohammed (17301920), Joost Dijkstra (1251785),Edward Tandia (17310806)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, echo = FALSE, include = FALSE, message = FALSE}
source(here::here("Setup.R"))
```

```{r setup, include=FALSE}
# exercise 3 - bacteria

# Problem I have is related to ggplot + animation + the type of my features in df: 
# geom_path: Each group consists of only one observation. Do you need to adjust
# the group aesthetic?

```

```{r setup, include=FALSE}
# definie terms
n = 25 # number of bacteria
Zeros = c() # bacterium starting points x0,y0

# generate 25 random initial points x0,y0

for(i in 1:n){
    #get the 1st value of punif(-8,8) and append it to Zeros
    x_0 = runif(1000,min =-8,max = 8)[1]
    y_0 = runif(1000,min =-8,max = 8)[1]

    Zeros <- append(Zeros,c(x_0,y_0))
}
zeros_pts<-Zeros %>% matrix(nrow = 25,ncol = 2)
colnames(zeros_pts)<-c("x","y")

        
#parameters
time = seq(1,121,by=1)
my_values = c()
a = 0
b = 2
#S = runif(1000,min = a,max = b) # uniform distribution of bacteria
t = c(1:121) # iterations
#gamma = runif(121,min = 0,max = 2*pi)
#cos_sin = matrix(c(cos(gamma),sin(gamma)),nrow =121,ncol= 2)

# simulations # check it 
for(i in 1:n){
  k = zeros_pts[i,] # x0 y0 inital points a t = 0
  S = runif(1000,min = a,max = b) # u
  gamma = runif(121,min = 0,max = 2*pi)
  cos_sin = matrix(c(cos(gamma),sin(gamma)),nrow =121,ncol= 2)
  for(t in 1:121){
    f = k + S[t] *cos_sin[t,]  # find a way to do the iteration with f t+1
    my_values <- append(my_values,f)
  }
}
        
```
 
 
````{r setup, include=FALSE}
#create a dateframe with the values of my_values, colnames = x,y

df <-my_values %>% split(f = c('x','y')) %>% data.frame()
        
# each letter = 1 bacteria simulations 
A=df[1:121,]
A[1,] <- c(zeros_pts[1,])
B=df[122:242,]
B[1,]<- c(zeros_pts[2,])
C=df[243:363,]
C[1,]<- c(zeros_pts[3,])
D=df[364:484,]
D[1,]<- c(zeros_pts[4,])
E=df[485:605,]
E[1,]<- c(zeros_pts[5,])
F=df[606:726,]
F[1,]<- c(zeros_pts[6,])
G=df[727:847,]
G[1,]<- c(zeros_pts[7,])
H=df[848:968,]
H[1,]<- c(zeros_pts[8,])
I=df[969:1089,]
I[1,]<- c(zeros_pts[9,])
J=df[1090:1210,]
J[1,]<- c(zeros_pts[10,])
K=df[1211:1331,]
K[1,]<- c(zeros_pts[11,])
L=df[1332:1452,]
L[1,]<- c(zeros_pts[12,])
M=df[1453:1573,]
M[1,]<- c(zeros_pts[13,])
N=df[1574:1694,]
N[1,]<- c(zeros_pts[14,])
O=df[1695:1815,]
O[1,]<- c(zeros_pts[15,])
P=df[1816:1936,]
P[1,]<- c(zeros_pts[16,])
Q=df[1937:2057,]
Q[1,]<- c(zeros_pts[17,])
R=df[2058:2178,]
R[1,]<- c(zeros_pts[18,])
S=df[2179:2299,]
S[1,]<- c(zeros_pts[19,])
T=df[2300:2420,]
T[1,]<- c(zeros_pts[20,])
U=df[2421:2541,]
U[1,]<- c(zeros_pts[21,])
V=df[2542:2662,]
V[1,]<- c(zeros_pts[22,])
W=df[2663:2783,]
W[1,]<- c(zeros_pts[23,])
X=df[2784:2904,]
X[1,]<- c(zeros_pts[24,])
Y=df[2905:3025,]
Y[1,]<- c(zeros_pts[25,])

# change colnames
colnames(A)<-c('x1','y1')
colnames(B)<-c('x2','y2')
colnames(C)<-c('x3','y3')
colnames(D)<-c('x4','y4')
colnames(E)<-c('x5','y5')
colnames(F)<-c('x6','y6')
colnames(G)<-c('x7','y7')
colnames(H)<-c('x8','y8')
colnames(I)<-c('x9','y9')
#colnames(df_11$x7.1)<-c('x10')
colnames(K)<-c('x11','y11')
colnames(L)<-c('x12','y12')
colnames(M)<-c('x13','y13')
colnames(N)<-c('x14','y14')
colnames(O)<-c('x15','y15')
colnames(P)<-c('x16','y16')
colnames(Q)<-c('x17','y17')
colnames(R)<-c('x18','y18')
colnames(S)<-c('x19','y19')
colnames(T)<-c('x20','y20')
colnames(U)<-c('x21','y21')
colnames(V)<-c('x22','y22')
colnames(W)<-c('x23','y23')
colnames(X)<-c('x24','y24')
colnames(Y)<-c('x25','y25')

df_1 <- cbind(A,B,C,D,E,F,G,H,I,G,K,L,M,N,O,P,Q,R,S,T,U,V,W,X,Y)

# loading image for the plot 
ovni = c('alien_image2.png')
df_11<-df_1 %>% mutate(image = ovni)  
````

``````{r setup, include=FALSE}
## plots         

#use geom_circle to plot a circle of radius 3 centered at (0,0) title the circle 'SUGAR'
staticplot<-ggplot() +
  geom_circle(aes(x0 = 0, y0 =0,r = 3), color = "orange", fill ='orange') +
  geom_text(aes(x=0,y=0,label = "SUGAR"),size = 15,color = 'white') +
  geom_line(data = df_11,aes(x=x1,y=y1,group = 1),color =1)+
  geom_line(data = df_11,aes(x=x2,y=y2,group=2),color =2)+
  geom_line(data = df_11,aes(x=x3,y=y3))+
  geom_line(data = df_11,aes(x=x5,y=y5),color =4)+
  geom_line(data = df_11,aes(x=x4,y=y4),color =3)+
  geom_line(data = df_11,aes(x=x6,y=y6),color =5)+
  geom_line(data = df_11,aes(x=x7,y=y7),color =6)+
  geom_line(data = df_11,aes(x=x8,y=y8),color =7)+
  geom_line(data = df_11,aes(x=x9,y=y9),color =8)+
  geom_line(data = df_11,aes(x=x7.1,y=y7.1),color =9)+
  geom_line(data = df_11,aes(x=x11,y=y11),color =10)+
  geom_line(data = df_11,aes(x=x12,y=y12),color =11)+
  geom_line(data = df_11,aes(x=x13,y=y13),color =12)+
  geom_line(data = df_11,aes(x=x14,y=y14),color =13)+
  geom_line(data = df_11,aes(x=x15,y=y15),color =14)+
  geom_line(data = df_11,aes(x=x16,y=y16),color =15)+
  geom_line(data = df_11,aes(x=x17,y=y17),color =16)+
  geom_line(data = df_11,aes(x=x18,y=y18),color =17)+
  geom_line(data = df_11,aes(x=x19,y=y19),color =18)+
  geom_line(data = df_11,aes(x=x20,y=y20),color =19)+
  geom_line(data = df_11,aes(x=x21,y=y21),color=20)+
  geom_line(data = df_11,aes(x=x22,y=y22),color =21)+
  geom_line(data = df_11,aes(x=x23,y=y23),color =22)+
  geom_line(data = df_11,aes(x=x24,y=y24),color =23)+
  geom_line(data = df_11,aes(x=x25,y=y25),color =24)+
  geom_image(data=df_11,aes(x=x1,y=y1,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x2,y=y2,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x3,y=y3,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x4,y=y4,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x5,y=y5,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x6,y=y6,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x7,y=y7,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x8,y=y8,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x9,y=y9,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x7.1,y=y7.1,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x11,y=y11,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x12,y=y12,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x13,y=y13,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x14,y=y14,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x15,y=y15,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x16,y=y16,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x17,y=y17,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x18,y=y18,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x19,y=y19,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x20,y=y20,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x21,y=y21,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x22,y=y22,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x23,y=y23,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x24,y=y24,image = image),size =0.05)+
  geom_image(data=df_11,aes(x=x25,y=y25,image = image),size =0.05)+
  xlim(-10,10) +
  ylim(-10,10) +
  xlab("X Position") +
  ylab("Y Position") +
  theme_bw()+
  ggtitle("Bacteria Motility") + theme(plot.title = element_text(hjust = 0.5))

````

```{r setup, include=FALSE}
#animation of the plot
staticplot+ transition_reveal(time)
```
